Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-04 PAPER/main.tex
minor changes section 3

Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, i.e. the values cannot be changed, and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle. Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.

@@

The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order of indices, and the higher-indexed vertices are in decreasing order of indices, i.e. $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$. Any edges that cannot be placed in such an order are then removed from this list. For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order. This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MCM, as $(v_5, v_{10}) \in B$.

Starting from the first edge, BR searches through the list to find an edge that meets the following conditions: 
\begin{enumerate*}[label={(\alph*)}]
	\item The lower-indexed vertex of the current edge, and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item The current edge and the next edge are members of different components on $G'$.
\end{enumerate*}

@@

\begin{figure}	
	\centering
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpsconnect}
		\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
		\label{fig:mpsconnect}
	\end{subfigure}
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpscycle}
		\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
		\label{fig:mpscycle}
	\end{subfigure}
	\caption{Selected edges found using BR can be used to merge the components of $G'$ together, thus forming an alternating Hamiltonian cycle which corresponds to a feasible solution.}
	\label{fig:connect/cycle}
\end{figure}

@@

\subsection{Modified First-Fit Decreasing Heuristic (MFFD)}
\label{sec:mffd}
The \textsc{Modified First-Fit Decreasing} (MFFD) heuristic performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip. If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item. If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip. For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled regardless of the orientation of the item, and therefore the item cannot be feasibly packed onto the strip.

@@

The \textsc{Pair-Smallest} (PS) heuristic is an extension of a procedure defined by \cite{lewis2011}. Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly. Each strip is initialised by choosing the item from $\mathcal{I}$ with the smallest score width, and packing it in a regular orientation. PS then continues to fill the strip by selecting the item with the smallest score width that meets the vicinal sum constraint with the right-most score width on the strip, and whose width will not cause the strip to be overfilled. This heuristic aligns the smallest score widths with the largest ones, eliminating the possibility of placing larger score widths together unecessarily. Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated.
% Break ties by choosing item whose second score width is larger.

\begin{itemize}
	\item \cite{lewis2011}
	\item Pack each strip one by one
	\item choose item with smallest score width that meets VSC with right-most score width on the strip, then check if the item can fit onto the strip
	\item if not, then choose item with second smallest score width that meets VSC, etc.
	\item when no more items can fit onto strip/no item can meet VSC with right-most score width on the strip, close the strip (no more items canbe placed on it) and start new strip
	\item If two items have equal score width, break ties by choosing item whose second score width is larger
	\item this method aligns smallest score widths with larger ones, eliminates possibility of aligning larger score widths together unecessarily.
	\item Heuristic prioritises VSC over item widths, chooses item with smallest possible score width that meets VSC first before checking item width.
\end{itemize}

>>>>

Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, i.e. the values cannot be changed and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle. Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.

@@

The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e. $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$. Any edges that cannot be placed in such an order are then removed from this list. For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order. This is due to $v_5$ not being matched with the highest-indexed vertex available $v_{10}$ during MCM, as $(v_5, v_{10}) \in B$.

Starting from the first edge, BR searches through the list to find an edge that meets the following conditions: 
\begin{enumerate*}[label={(\alph*)}]
	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item The current edge and the next edge are members of different components on $G'$.
\end{enumerate*}

@@

\begin{figure}	
	\centering
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpsconnect}
		\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
		\label{fig:mpsconnect}
	\end{subfigure}
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpscycle}
		\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
		\label{fig:mpscycle}
	\end{subfigure}
	\caption{Selected edges found using BR merge the components of $G'$ together, forming an alternating Hamiltonian cycle which corresponds to a feasible solution $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.}
	\label{fig:connect/cycle}
\end{figure}

@@

\subsection{Modified First-Fit Decreasing Heuristic (MFFD)}
\label{sec:mffd}
The \textsc{Modified First-Fit Decreasing} (MFFD) heuristic performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip. If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item. If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip. For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled in either orientation of the item, and therefore it cannot be feasibly packed onto the strip.

@@

The \textsc{Pair-Smallest} (PS) heuristic is an extension of a procedure defined by \cite{lewis2011}. Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly. Each strip is initialised by choosing the item from $\mathcal{I}$ with the smallest score width, and packing it in a regular orientation. PS then continues to fill the strip by selecting the item with the smallest score width that meets the vicinal sum constraint with the right-most score width on the strip, and whose width will not cause the strip to be overfilled. This heuristic aligns the smallest score widths with the largest ones, eliminating the possibility of placing larger score widths together unecessarily. Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated. If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
% Break ties by choosing item whose second score width is larger.
% If item with smallest feasible score width does not fit onto the strip, choose item with next smallest score width and repeat.
